A fault tolerant multi-server system for MMOGs

### 2011-07-07 textos/phd-prospectus/prospectus.tex
prospectus ready for being reviewed by the advisor

The rest of this document is organized as follows: Section \ref{sec:mmogserver} describes the basic features of an MMOG server; Section \ref{sec:distserver} introduces our proposed distributed server model and describes briefly some of its protocols; Section \ref{sec:futurework} presents the research directions to be followed next and Section \ref{sec:achievements} lists some of the accomplishments achieved by this research so far.

@@

Figure \ref{fig:consistency} illustrates two avatars situated in regions managed by different server groups, but still close enough to interact. Each command issued by their players has to be forwarded to the groups that manage some object in its target set, which is done by multicast.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\linewidth]{images/consistency}
  \caption{Multicasting a command to a group which manages an object in that command's target set}
  \label{fig:consistency}
\end{figure}

@@

@@

We are currently workings towards the validation of both the optimistic multicast

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activities and publications} \label{sec:achievements}

Some related work that we have published so far include:
%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The rest of this document is organized as follows: Section \ref{sec:mmogserver} describes the basic features of an MMOG server; Section \ref{sec:distserver} introduces our proposed distributed server model and describes briefly some of its protocols; Section \ref{sec:achievements} lists some of the works we published so far and Section \ref{sec:futurework} presents the research directions to be followed next.

@@

% Figure \ref{fig:consistency} illustrates two avatars situated in regions managed by different server groups, but still close enough to interact. Each command issued by their players has to be forwarded to the groups that manage some object in its target set, which is done by multicast.
% 
% \begin{figure}[!h]
%   \centering
%   \includegraphics[width=0.8\linewidth]{images/consistency}
%   \caption{Multicasting a command to a group which manages an object in that command's target set}
%   \label{fig:consistency}
% \end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Published work} \label{sec:achievements}

Some related work that we have published so far include:
\begin{itemize}
  \item C. E. B. Bezerra, J. L. D. Comba, C. F. R. Geyer. A fine granularity load balancing technique for MMOG servers using a kd-tree to partition the space. \textit{VIII Brazilian Symposium on Computer Games and Digital Entertainment - Computing Track}, 2009.
  \item C. E. B. Bezerra, C. F. R. Geyer. A load balancing scheme for massively multiplayer online games. \textit{Multimedia Tools and Applications - Special Issue on Massively Multiplayer Online Gaming Systems and Applications}, v. 1, n. 1, pp. 263-289, 2009.
  \item C. E. B. Bezerra, F. R. Cecin, C. F. R. Geyer. A3: a novel interest management algorithm for distributed simulations of MMOGs. \textit{12-th IEEE International Symposium on Distributed Simulation and Real Time Applications}, 2008.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We are currently workings towards the validation of both the quasi-genuine multicast and the game state consistency management protocols, which require both formal proofs regarding correctness and experimental results to demonstrate their performance. Another direction that we intend to follow is to consider not only crash-stop faults, but also Byzantine faults. By tolerating these faults, the server system would also be resistant to cheating, which can also be seen as Byzantine behavior.

@@
